Implementing Change in Multi-paradigm Environments, a Case Study

### 2015-02-17 rmtw/a3/latex8.tex
Changes in validity section
Y O L O

However, there are is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms.

@@

\SubSection{Research Question(s)}
RQ: How is change managed in multi-paradigm environments?

@@

While designing the study, validity concerns were taken into consideration. The most pressing of which would be the limited scope of the study. The fact that the study only occurred in a subset of Ericsson and not a larger part of the company means that we cannot reliably make any generalities about the results. This is something that could be overcome during a potential triangulation period. For example, further studies could be conducted within Ericsson at other departments which could then be used to strengthen or diminish the results from this study.

@@

We have re-used some material from our DIT037 course. (Mostly in literature review and case company description). Because of this some of the text might show up on Urkund. For the most important parts, such as methodology and research questions we have not used any material from our DIT035 paper.

>>>>

However, there is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms.

@@

\SubSection{Research Questions}
RQ: How is change managed in multi-paradigm environments?

@@

While designing the study, validity concerns were taken into consideration. The most pressing of which would be the limited scope of the study. The fact that the study only occurred in a subset of Ericsson and not a larger part of the company means that we cannot reliably make any generalities about the results. This is something that could be overcome during a potential triangulation period. For example, further studies could be conducted within Ericsson at other departments which could then be used to strengthen or diminish the results from this study. Furthermore, our study only involved model driven development and manual coding. As such we cannot generalise about the applicability concerning other paradigms.

@@

We have re-used some material from our DIT037 course. (Mostly in literature review and case company description). Because of this some of the text might show up on Urkund. For the most important parts, such as methodology and research questions we have not used any material from our DIT037 paper.
